### 2019-04-15 paper/paper.tex
added conclusion

This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} 
that performs extensive analysis of the \emph{node package manager} (\code{npm}) ecosystem. 
\code{npm} provides a set of open source tools that allow developers to 
describe packages for \code{Node.js}, an asynchronous JavaScript runtime environment 
designed for network applications\footnote{https://nodejs.org/en/about/}.
The services provided by \code{npm} include a command line interface for maintaining 
\code{package.json} files, the primary method to describe package metadata such as the name,
description, version, and dependencies of a given package. \code{npm} also allows 
developers to publish their packages to a public registry, permitting anyone 
to download and use their software. Packages hosted on \code{npm} will often depend on other \code{npm}
packages, forming an elaborate JavaScript package ecosystem.
Since the publishing of the original paper, the usage and scale of \code{npm} has only grown,
and now hosts more than three times as many packages (over 750,000 as of April 1\textsuperscript{st} 2019) 
and handles over ten times as many weekly package downloads (now over ten billion per week).
Additionally, the major frameworks used in JavaScript development have undergone a 
rapid transformation as packages such as Angular and React are adopted\footnotemark{\ref{adoption}}.
The core contributions we make are as follows:
\begin{itemize}
  \item We replicate and verify the results found in the original paper for the 
    window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 
    2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends 
    noted in the original paper are still observable.
  \item We investigate whether the continued evolution of the JavaScript package 
    ecosystem has affected the relationships between various measures of package popularity.
  \item We determine if the ongoing maturation of the \code{npm} ecosystem has 
    resulted in tangible changes to version numbering or adoption practices.
\end{itemize}

@@

\section{Version Numbering and Package Adoption}
[NEEDS MORE DATA]

\subsection{Attribution of Version Numbers}
[NEEDS MORE DATA

\subsection{Adoption by Version Number}
[NEEDS MORE DATA]

@@

Related research can be generally described as one of two types
of work: meta-analyses of the behaviour and importance
of software ecosystems, and empirical investigations into the
specifics of a particular ecosystem. Some topics 
for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such
paper and the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
who present a dataset with basic metrics, dependencies and changes within the popular 
Java-based Maven ecosystem. Another work investigates the
result of changing project interdependencies in Apache \cite{Bavota:2013}, 
and still others evaluate evolution over time in ecosystems such as
Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.

\section{Conclusion}
[NEEDS MORE DATA]

>>>>

This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} 
that performs extensive analysis of the \emph{node package manager} (\code{npm}) ecosystem. 
\code{npm} provides a set of open source tools that allow developers to 
describe packages for \code{Node.js}, an asynchronous JavaScript runtime environment 
designed for network applications\footnote{https://nodejs.org/en/about/}.
The services provided by \code{npm} include a command line interface for maintaining 
\code{package.json} files, the primary method to describe package metadata such as the name,
description, version, and dependencies of a given package. \code{npm} also allows 
developers to publish their packages to a public registry, permitting anyone 
to download and use their software. Packages hosted on \code{npm} will often depend on other \code{npm}
packages, forming an elaborate JavaScript package ecosystem.
Since the publishing of the original paper, the usage and scale of \code{npm} has only grown,
and now hosts more than three times as many packages (over 750,000 as of April 1\textsuperscript{st} 2019) 
and handles over ten times as many weekly package downloads (now over ten billion per week).
Additionally, the major frameworks used in JavaScript development have undergone a 
rapid transformation as packages such as Angular and React are adopted\footnotemark{\ref{adoption}}.
The core contributions we make are as follows:
\begin{itemize}
  \item We replicate and verify the results found in the original paper for the 
    window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 
    2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends 
    noted in the original paper are still observable.
  \item We investigate whether the continued evolution of the JavaScript package 
    ecosystem has affected the relationships between various measures of package popularity.
  % \item We determine if the ongoing maturation of the \code{npm} ecosystem has 
  %   resulted in tangible changes to version numbering or adoption practices.
\end{itemize}

@@

% \section{Version Numbering and Package Adoption}
% [NEEDS MORE DATA]

% \subsection{Attribution of Version Numbers}
% [NEEDS MORE DATA

% \subsection{Adoption by Version Number}
% [NEEDS MORE DATA]

@@

Related research can be generally described as one of two types
of work: meta-analyses of the behaviour and importance
of software ecosystems, and empirical investigations into the
specifics of a particular ecosystem. Some topics 
for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such as this
paper as well as the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
who present a dataset with basic metrics, dependencies and changes within the popular 
Java-based Maven ecosystem. Another work investigates the
result of changing project interdependencies in Apache \cite{Bavota:2013}, 
and still others evaluate evolution over time in ecosystems like
Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.

\section{Conclusion}

In this paper, we take a second look at the \code{npm} ecosystem,
replicating and extending the results of previous research by 
Wittern, Suter and Rajagopalan \cite{Wittern:2016}. Though
we observe that the growth of \code{npm} has slowed down, the ecosystem
continues to thrive, demonstrating signs of maturity rather than decline.

Contrary to the trend observed in the original paper, there appears to be
some effort to reduce the number of inter-package dependencies, and therefore the risks
associated with complex dependency trees. The core set of packages upon which
multiple other projects rely on has remained relatively constant in size, and
demonstrates a trend towards even further concentration. Accordingly, the set of packages
most depended on in the \code{npm} ecosystem is also trending towards stability, with
fewer and fewer packages entering the top ranks each year.

Our results regarding relationships between popularity metrics support the discoveries of the
original paper, further reinforcing the theory that packages can be generally divided into the categories
of end user and core utility packages, and improving our understanding of how package popularity evolves.
Ultimately, our second evaluation of the \code{JavaScript} package environment can help developers evaluate
the state of the \code{npm} ecosystem, and continue to make informed decisions when selecting frameworks
to use in their applications.
